Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-10-19 code/analysis.Rmd
updated compplot

plotcomp <- final %>%
  filter(dowel_density != "0000") %>%
  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
  ggplot(aes(x = Re, y = eta, ymin = eta - deta, ymax = eta + deta, color = factor(phi, labels = c("0.22%","0.64%","1.17%")))) +
  geom_line(data = fauria_pred, aes(y = eta_est, x = Re, linetype = "Fauria et al. model"), inherit.aes = FALSE, show.legend = TRUE) +
  geom_point() +
  geom_errorbar(width = 20) +  
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~ as.character(round(phi,5))) +
  labs(y = "ECE", x = expression(Re[c]), color = expression(phi[c])) +
  theme_bw() +
  scale_linetype_discrete(name = "") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "bottom") +
  guides(fill = guide_legend(override.aes = list(linetype = 0)),
         color = guide_legend(override.aes = list(linetype = 0)))

>>>>

plotcomp <- final %>%
  filter(dowel_density != "0000") %>%
  mutate(Refac = factor(Re, labels = c("Re = 66.78", "Re = 133.56", "Re = 200.34"))) %>%
  ggplot(aes(x = Re, y = eta, ymin = eta - deta, ymax = eta + deta, color = factor(phi, labels = c("0.22%","0.64%","1.17%")))) +
  geom_line(data = fauria_pred, aes(y = eta_est, x = Re, linetype = "Fauria et al. model"), inherit.aes = FALSE, show.legend = TRUE) +
  geom_point() +
  geom_errorbar(width = 10) +  
  scale_y_log10(labels = scales::percent) +
  facet_wrap(~ as.character(round(phi,5))) +
  labs(y = "ECE", x = expression(Re[c]), color = expression(phi[c])) +
  theme_bw() +
  scale_linetype_discrete(name = "") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "bottom") +
  guides(fill = guide_legend(override.aes = list(linetype = 0)),
         color = guide_legend(override.aes = list(linetype = 0)))

plotcomp
